Why do species get a thin slice of $\pi$? Revisiting Lewontin's Paradox of Variation

### 2021-05-11 manuscript/manuscript.tex
updated figures

  \caption{The regression estimates of full IUCN Red List population size model
    for diversity, $\log_{10}(\pi) = \beta_0 + \beta_{LC} LC + \beta_{NT} NT +
    \beta_{VU} VU + \beta_{EN} EN + \beta_{CR} CR + \beta_{N_c} \log_{10}(N_c)$;
    $df = 165$.  Using AIC to compare this full model to a reduced model of
    $\log_{10}(\pi) = \beta_0 + \beta_{N_c} \log_{10}(N_c)$, $AIC_\text{full} =
  203.99$, $AIC_\text{reduced} =212.46$. }

>>>>

  \caption{TODO The regression estimates of full IUCN Red List population size model
    for diversity, $\log_{10}(\pi) = \beta_0 + \beta_{LC} LC + \beta_{NT} NT +
    \beta_{VU} VU + \beta_{EN} EN + \beta_{CR} CR + \beta_{N_c} \log_{10}(N_c)$;
    $df = 165$.  Using AIC to compare this full model to a reduced model of
    $\log_{10}(\pi) = \beta_0 + \beta_{N_c} \log_{10}(N_c)$, $AIC_\text{full} =
  203.99$, $AIC_\text{reduced} =212.46$. }
